Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-28 article/06_Supplementary_Remarks.Rmd
dating accuracy: literature

Another aspect to consider concerning the data quality is the temporal accuracy of the radiocarbon dating. Ideally each radiocarbon date represents the exact point in time of the creation of the respective grave. Unfortunately several natural and cultural effects can cause a (partially systematic) offset between the radiocarbon date and the burial ceremony, including the *Marine reservoir effect*, the *Old wood effect*, the *Human ^14^C-residence ("adult") effect* or cultural practices like a secondary treatment of the body or the deposition of burial objects that are already ancient at the time of the ceremony. These effects can have strong influence on the accuracy of the dating information, but can only be explored for each grave individually. In the present paper they therefore had to be ignored.

>>>>

Another aspect to consider concerning the data quality is the temporal accuracy of the radiocarbon dating. Ideally each radiocarbon date represents the exact point in time of the creation of the respective grave. Unfortunately several natural and cultural effects can cause a (partially systematic) offset between the radiocarbon date and the burial ceremony, including the *Marine reservoir effect* [@Ascough2005], the *Old wood effect* [@OLSEN201330], the *Human ^14^C-residence ("adult") effect* [@Hedges2007] or cultural practices like a secondary treatment of the body or the deposition of burial objects that are already ancient at the time of the ceremony. These effects can have strong influence on the accuracy of the dating information, but can only be explored for each grave individually. In the present paper they therefore had to be ignored.
